Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-01-26 docs/manuscript/manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility and reproducibility enhancing research practices.
Table 1 presents our summary measures for each topic, as well as those measures by subgroup.

@@

%%%%%%%%%%%
\subsubsection*{Definition of Reproducibility}
Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

@@

\begin{table}[h]
    \centering
    \begin{threeparttable}
    \caption{Barriers to Reproducibility}
    \begin{tabular}{l c c c c c c c c c c}
         \hline
                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
         Barrier    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
         \hline
         \textit{Research Environment}      & & & & & & & & & & \\
         Pressure to Publish                & 61.2\% & 83.1\% & 54.5\% & 75.0\% & & & & & & 71.5\% \\
         Insufficient oversight             & 56.7\% & 81.6\% & 63.6\% & 82.0\% & & & & & & 71.1\% \\
         Fraud                              & 22.4\% & 32.3\% & 9.1\%  & 39.3\% & & & & & & 28.4\% \\
                                            & & & & & & & & & &\\
         \textit{Artifact Availability}     & & & & & & & & & & \\
         Insufficient metadata              & 62.6\% & 76.9\% & 59.1\% & 78.7\% & & & & & & 80.2\% \\
         Unavailable Data                   & 65.7\% & 89.3\% & 59.1\% & 78.6\% & & & & & & 75.2\% \\
         Unavailable protocol/code          & 59.7\% & 77.0\% & 50.0\% & 86.9\% & & & & & & 71.1\% \\
         Published incomplete results       & 56.7\% & 73.8\% & 63.7\% & 78.7\% & & & & & & 68.4\% \\
         Use restricted data/software       & 44.8\% & 56.9\% & 40.9\% & 82.0\% & & & & & & 57.8\% \\
                                            & & & & & & & & & &\\
         \textit{Study Characteristics}     & & & & & & & & & & \\
         Geographic variation               & 61.2\% & 80.0\% & 81.8\% & 72.2\% & & & & & & 71.5\% \\
         Researcher positionality           & 70.2\% & 50.8\% & 72.8\% & 70.5\% & & & & & & 64.2\% \\
         Chance                             & 55.2\% & 66.2\% & 68.2\% & 65.6\% & & & & & & 62.3\% \\
         Different computation              & 38.8\% & 53.8\% & 31.8\% & 68.9\% & & & & & & 50.9\% \\
                                            & & & & & & & & & &\\
         N                                  & 67 & 65 & 22 & 61 & & 92 & 40 & 85 & & 218 \\
        \hline
    \end{tabular}
    \begin{tablenotes}
        \footnotesize
        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods. 
        \item Percentage of respondents reporting each factor frequently or occasionally contributed to a lack of reproducibility in geographic research
    \end{tablenotes}
    \label{tab:barriers}
    \end{threeparttable}
\end{table}

Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
A high percentage of physical, methods-focused, and quantitative geographers identified these factors as barriers. 
Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
Contrary to alarms raised in some of the reproducibility literature, a minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.

Researchers identified the unavailability of research artifacts (e.g., data, code) as a barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility than did human and nature-society researchers.
A similar gap existed between qualitative and mixed-methods researchers and qualtiative researchers. 
The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibility, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor. 
Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.

A majority of researchers identified geographic variation (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researcher across subfields and approaches. 
A smaller percentage of physical geographers placed less emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
Differences between the computational environment used to conduct and original study and a reproduction attempt was generally not seen as a common factor contributing to a lack of reproducibility in the discipline. 
The exception being methods-focused (68.9\%) and quantitative researchers (\%), which aligns with the research practices used in these areas of research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.

WHY DID RESEARCHERS ATTEMPT REPRODUCTION - Q10

ACCESS MATERIALS - Q12.
The majority of researchers (82/102) that attempted reproductions were able to access at least some of the data used in the original study, but only (27/102) could access all of the original data.

OUTCOME - Q11 AND OUTCOME BY ACCESS Q12
Geographic researchers report being able to recreate some the results they attempt to reproduce, but few researchers report being able to identically recreate all results (20/102).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility enhancing research practices.
Table 1 presents our summary measures for each topic, as well as those measures by subgroup.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

In aggregate, respondents identified reproducibility as an important means of achieving numerous epistemic goals in geographic research (Q17).
\begin{itemize}
    \item reducing the risk of persistent errors (77.5\%)
    \item preventing duplication of research efforts (63.3\%)
    \item communicating results to academics (68.8\%)
    \item communicating results to practitioners (64.7\%)
    \item Researchers also view attempting reproductions as an important part of student training (75.7\%). 
\end{itemize}

Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to quantitiative or mixed-methods researchers.

@@

\begin{table}[h]
    \centering
    \begin{threeparttable}
    \caption{Barriers to Reproducibility}
    \begin{tabular}{l c c c c c c c c c c}
         \hline
                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
         Barrier    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
         \hline
         \textit{Research Environment}      & & & & & & & & & & \\
         Pressure to Publish                & 61.2\% & 83.1\% & 54.5\% & 75.0\% & & 77.3\% & 47.5\% & 75.3\% & & 71.5\% \\
         Insufficient oversight             & 56.7\% & 81.6\% & 63.6\% & 82.0\% & & 82.6\% & 40.0\% & 74.2\% & & 71.1\% \\
         Fraud                              & 22.4\% & 32.3\% & 9.1\%  & 39.3\% & & 29.4\% & 20.0\% & 31.8\% & & 28.4\% \\
                                            & & & & & & & & & &\\
         \textit{Artifact Availability}     & & & & & & & & & & \\
         Insufficient metadata              & 62.6\% & 76.9\% & 59.1\% & 78.7\% & & 79.4\% & 45.0\% & 72.9\% & & 80.2\% \\
         Unavailable Data                   & 65.7\% & 89.3\% & 59.1\% & 78.6\% & & 87.0\% & 42.5\% & 81.2\% & & 75.2\% \\
         Unavailable protocol/code          & 59.7\% & 77.0\% & 50.0\% & 86.9\% & & 87.0\% & 37.5\% & 70.6\% & & 71.1\% \\
         Published incomplete results       & 56.7\% & 73.8\% & 63.7\% & 78.7\% & & 78.2\% & 37.2\% & 72.9\% & & 68.4\% \\
         Use restricted data/software       & 44.8\% & 56.9\% & 40.9\% & 82.0\% & & 70.7\% & 32.5\% & 56.5\% & & 57.8\% \\
                                            & & & & & & & & & &\\
         \textit{Study Characteristics}     & & & & & & & & & & \\
         Geographic variation               & 61.2\% & 80.0\% & 81.8\% & 72.2\% & & 79.4\% & 40.0\% & 74.1\% & & 71.5\% \\
         Researcher positionality           & 70.2\% & 50.8\% & 72.8\% & 70.5\% & & 56.5\% & 80.0\% & 65.9\% & & 64.2\% \\
         Chance                             & 55.2\% & 66.2\% & 68.2\% & 65.6\% & & 67.4\% & 52.5\% & 64.4\% & & 62.3\% \\
         Different computation              & 38.8\% & 53.8\% & 31.8\% & 68.9\% & & 63.1\% & 25.0\% & 56.5\% & & 50.9\% \\
                                            & & & & & & & & & &\\
         N                                  & 67 & 65 & 22 & 61 & & 92 & 40 & 85 & & 218 \\
        \hline
    \end{tabular}
    \begin{tablenotes}
        \footnotesize
        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods. 
        \item Percentage of respondents reporting each factor frequently or occasionally contributed to a lack of reproducibility in geographic research
    \end{tablenotes}
    \label{tab:barriers}
    \end{threeparttable}
\end{table}

Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
A high percentage of physical, methods-focused, quantitative, and mixed-methods researchers identified these factors as barriers. 
Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
Contrary to alarms raised in some of the reproducibility literature, a minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.

Researchers identified the unavailability of research artifacts (e.g., data, code) as a barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
A similar gap existed between qualitative researchers and those identifying as mixed-methods researchers or quantitative researchers. 
The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibility, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor. 
Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantiative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.

A majority of researchers identified geographic variation (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches. 
A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
Differences between the computational environment used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline. 
The exception being methods-focused (68.9\%) and quantitative researchers (63.1\%\%), which aligns with the research practices used in these areas of research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
Approximately half (49\%) of the researchers attempting reproductions reported submitting their findings for publication.

WHY DID RESEARCHERS ATTEMPT REPRODUCTION - Q10
\begin{itemize}
    \item to check results - surprising, as part of peer-review, of related interest
    \item to check their own results and make them more accessible
    \item to learn more about methods and/or transfer them into their own work
\end{itemize}

In most instances, researchers reported some ability to access the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.  
The majority of researchers that attempted reproductions (82\%) were able to access at least some of the data used in the original study, but few researchers (27\%) reported access to all of the original data.
Researchers also reported the ability to access at least some information about study procedures (69\%) and its computational environment (60\%), but limited ability to access all procedural (20\%) and computational information (15\%). 
Nearly all researchers reported at least partially reproducing some results (96\%), but less than half reported being able to at least partially reproduce all results (38\%).
Few researchers were able to identically reproduce all results (20\%).

How much access researchers had to study data and procedural information impacted their ability to reproduce results. 
If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in all cases, but were able at least partially reproduce all results less than half of the time (42.9\%).
With complete access to all data and procedures, researchers reported the ability to at least partially reproduce all results 68.4 percent of the time.
Accessibility to data and procedures appears to be equally important in raising the chances of reproducing all results. 
Given access to some or all procedural information, having access to all data doubled a researcher's chances of reproducing all results (69.5\%) when compared to having access to only some of the data (27.5\%). 
We observed the same doubling effect when reversing this relationship. 
Given access to some or all of a study's data, having access to all the procedural information doubled a researcher's chances of reproducing all results (70.0\%) when compared to having access to only some of the procedures (30.0\%).
